Supplementary Information

### 2021-02-08 doc/manuscript/MEE_manuscript.Rmd
update schematic figure
#110

![**Figure 1 | DRAFT Schematic illustrating our analysis process.** This analysis was conducted separately for each site (step 1) and species (step 2).](tables_figures/schematic_figure.png)

>>>>

![**Figure 1 | Schematic illustrating our analysis process.** In step 1,the R package *climwin* [@van_de_pol_identifying_2016] is used to identify the most important climate drivers in water and temperature variable groups for each site. In step 2, a GLS model is used to produce a combined model with drivers, reconstructed DBH, and year.  (STILL NEED TO FIX THE PLOTS ON THIS.)](tables_figures/schematic_figure.png)
